\documentclass{article}[18pt]
\input{../format}
\lhead{AZ900}


\begin{document}
\begin{center}
\underline{\huge Azure Data Storage Options}
\end{center}
\section{Benefits of storing data in the cloud}
\begin{itemize}
	\item Automated backup and recovery
	\item Replication across the globe
	\item Support for data analytics
	\item Encryption capabilities
	\item Multiple data types
	\item Data storage in virtual disks
	\item Storage tiers
\end{itemize}
\subsection{Types of data}
\begin{definition}[Structured data]
	Data that adheres to a schema. Relational data
\end{definition}
\begin{definition}[Semi-strutured data]
	Using tags and keys to provide hierarchy. Used in NoSQL databases
\end{definition}
\begin{definition}[Unstructured data]
	Data with no designated structure
\end{definition}
\section{Azure Data storage}
\subsection{Azure SQL database}
Relational Database as a service. Based on Microsoft SQL Server database engine.\\
\\
Uses the Microsoft Data Migration Assistant to generate reports to guide through migration.
\subsection{Azure Cosmos DB}
Globally distributed database service supporting schema-less data (NoSQL). Used for highly responsive and always on applications
\subsection{Azure Blob storage}
Holds unstructured data
\subsection{Azure data lake}
Allows you to perform analytics on your data usage and prepare reports. Data lake is a large repository that stores both structured and unstructured data.
\subsection{Azure Files}
Offers fully managed file shares in the cloud over SMB (Server Message Block). 
\subsection{Azure Queue}
Used for storing large numbers of messages\\
\\
Can be used to:
\begin{itemize}
	\item Create a backlog of work and to pass messages between different Azure web servers
	\item Distribute load among different web servers/infrastructure and to manage bursts of traffic
	\item Build resilience against component failure when multiple users access your data at the same time
\end{itemize}
\subsection{Disk storage}
Provides disks for virtual machines and other services to access as they need. Come in many different sizes and performance levels, from SSDs to HDDs.
\subsection{Storage tiers}
Azure offers 3 storage tiers for blob object storage
\begin{enumerate}
	\item Hot storage - Accessed frequently
	\item Cool storage - Infrequent access
	\item Archive storage - Rarely accessed
\end{enumerate}
\subsection{Encryption and replication}
The following encryption types are available for your resources:
\begin{itemize}
	\item Azure Storage Service Encryption (SSE) - For data at rest. Encrypts before storing and decrypts during retrieval
	\item Client side encryption - Data already encrypted by the client libraries. Decrypted during retrieval
\end{itemize}
\section{Comparison with on premises storage}
{\renewcommand{\arraystretch}{2}
	\begin{tabularx}{\textwidth}{s b b}
		
		\textbf{Needs} & \textbf{On Premises} & \textbf{Azure data storage}\\
		\hline
		Compliance and security& Dedicated servers required for privacy and security& Client side encryption and encryption at rest\\
		\hline
		Store structured and unstructured data & Additional IT resources with dedicated servers required& Azure data lake and portal analyses and manages all types of data\\
		\hline
		Replication and high availability& More resources, licensing and servers required& Built in replication and redundancy features available\\
		\hline
		Application sharing and access to shared resources& File sharing requires additional administration resources& File sharing options without additional license\\
		\hline
		Relational data storage& Needs a database server with database admin role& Offers DBaaS options\\
		\hline
		Distributed storage and data access& Expensive storage, networking and compute resources needed& Azure Cosmos DB provides distributed access\\
		\hline
		Messaging and load balancing& Hardware redundancy impacts budget and resources& Azure Queue provides effective load balancing\\
		\hline
		Tiered storage& Management of tiered storage needs technology and labour skill set& Azure offers automated tiered storage of data
		
		
	\end{tabularx}
}
\end{document}
